A saturation model for impaired learning with enhanced plasticity: Supplementary material

### 2013-04-17 MHCpaper/MHCsupp.tex
updated plot parameters

\begin{table}
 \begin{center}
  \begin{tabularn}{|l|c|c|c|c|c|c|}
    \cline{1-7}
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
    \cline{1-7}
    Cascade       & 10 & $x=0.25$ & $x=0.33$ & -0.3  & 50 & 50  &\label{tr:cascade_short} \\
    Cascade       & 10 & $x=0.25$ & $x=0.33$ & -0.3  & 50 & 150 &\label{tr:cascade_long} \\
    Step-multistate    & 10 & $q=0.6$  & $q=0.8$  & -0.1  & 50 & 50  &\label{tr:multistate_weak} \\
    Step-multistate    & 10 & $q=0.6$  & $q=0.8$  & -0.17 & 10 & 30  &\label{tr:multistate_med} \\
    Step-multistate    & 10 & $q=0.6$  & $q=0.8$  & -0.4  & 20 & 20  &\label{tr:multistate_strong} \\
    Linear Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.3  & 20 & 20  &\label{tr:multistate_lin} \\
    Two-state     & 2  & $q=0.4$  & $q=0.8$  & -0.1  & 5  & 5   &\label{tr:binary} \\
    Pooled        & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
                                          & -0.1 & 70 & 70 &\label{tr:pooled_plenty}\\
    Pooled        & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
                                          & -0.1 & 70 & 70 &\label{tr:pooled_scarce}\\
    \cline{1-7}
%   \hline
%    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
%    & Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
%    \cline{1-7}
%    \label{tr:cascade_short}&
%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50   \\
%    \label{tr:cascade_long}&
%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150  \\
%    \label{tr:multistate_weak}&
%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50   \\
%    \label{tr:multistate_strong}&
%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20   \\
%    \label{tr:binary}&
%    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5  & 5    \\
%    \label{tr:pooled_plenty}&
%    Pooled     & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
%                                          & -0.1 & 70 & 70 \\
%    \label{tr:pooled_scarce}&
%    Pooled     & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
%                                          & -0.1 & 70 & 70 \\
%    \cline{1-7}
  \end{tabularn}
 \end{center}
  \caption{Parameters used in simulations.} \label{tab:params}
\end{table}

@@

\resultsfig{step-multistate}{moderate training}{($\Delta f=-0.17$)}{multistate_med}

\resultsfig{step-multistate}{strong training}{($\Delta f=-0.4$)}{multistate_strong}

@@

\resultsfig{pooled resource}{heavy depletion}{($q\lmin/q\lmax=0.25$)}{pooled_scarce}

@@

\resultsfig{cascade}{short pre-training}{($rt_\text{pre}=50$)}{cascade_short}

\resultsfig{cascade}{long pre-training}{($rt_\text{pre}=150$)}{cascade_long}

>>>>

\begin{table}
 \begin{center}
  \begin{tabularn}{|l|c|c|c|c|c|c|}
    \cline{1-7}
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
    \cline{1-7}
    Step-multistate    & 10 & $q=0.3$  & $q=0.4$  & -0.1  & 5 & 20  &\label{tr:multistate_weak} \\
    Step-multistate    & 10 & $q=0.3$  & $q=0.4$  & -0.3  & 5 & 20  &\label{tr:multistate_med} \\
    Step-multistate    & 10 & $q=0.3$  & $q=0.4$  & -0.45 & 5 & 30  &\label{tr:multistate_strong} \\
    Two-state          & 2  & $q=0.1$  & $q=0.2$  & -0.1  & 5 & 5   &\label{tr:binary} \\
    Linear Multistate  & 10 & $q=0.3$  & $q=0.4$  & -0.3  & 5 & 5   &\label{tr:multistate_lin} \\
    Pooled        & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
                                          & -0.1 & 5 & 20 &\label{tr:pooled_plenty}\\
    Pooled        & 10 & $q\in[0.05,0.4]$  & $q\in[0.1,0.8]$
                                          & -0.1 & 5 & 20 &\label{tr:pooled_scarce}\\
    Cascade       & 10 & $x=0.25$ & $x=0.33$ & -0.3  & 5 & 20  &\label{tr:cascade_short} \\
    Cascade       & 10 & $x=0.25$ & $x=0.33$ & -0.3  & 5 & 100 &\label{tr:cascade_long} \\
    \cline{1-7}
%   \hline
%    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
%    & Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
%    \cline{1-7}
%    \label{tr:cascade_short}&
%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50   \\
%    \label{tr:cascade_long}&
%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150  \\
%    \label{tr:multistate_weak}&
%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50   \\
%    \label{tr:multistate_strong}&
%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20   \\
%    \label{tr:binary}&
%    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5  & 5    \\
%    \label{tr:pooled_plenty}&
%    Pooled     & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
%                                          & -0.1 & 70 & 70 \\
%    \label{tr:pooled_scarce}&
%    Pooled     & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
%                                          & -0.1 & 70 & 70 \\
%    \cline{1-7}
  \end{tabularn}
 \end{center}
  \caption{Parameters used in simulations.} \label{tab:params}
\end{table}

@@

\resultsfig{step-multistate}{moderate training}{($\Delta f=-0.3$)}{multistate_med}

\resultsfig{step-multistate}{strong training}{($\Delta f=-0.45$)}{multistate_strong}

@@

\resultsfig{pooled resource}{heavy depletion}{($q\lmin/q\lmax=0.125$)}{pooled_scarce}

@@

\resultsfig{cascade}{short pre-training}{($rt_\text{pre}=20$)}{cascade_short}

\resultsfig{cascade}{long pre-training}{($rt_\text{pre}=100$)}{cascade_long}
